\vspace{-1.3cm} \textmd{\normalsize{High Performance Computing Project}}\\ Parallelization of the Probabilistic Roadmap Method with GPU Acceleration

### 2016-03-30 paper/paper.tex
robotsolution picture

\documentclass{scrartcl} 
\usepackage[ngerman,english]{babel}
 \usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[applemac]{inputenc}

@@

@@

\section{Results}

Tested have been made on a scenario with a robot with 4 joints. For creating and plotting the environment and the resulting trajectories, Matlab functions are provided.

@@

	- dependant on density of nodes: how many neighbours have to be tested per connection

>>>>

\documentclass{scrartcl} 
%\documentclass[a4paper]{article}
%\usepackage{a4wide}

\usepackage[ngerman,english]{babel}
 \usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[applemac]{inputenc}

@@

\usepackage{wrapfig}

@@

\newpage
\section{Results}

\begin{wrapfigure}{r}{0.5\textwidth}\label{robotsolution}
	\centering
	\includegraphics[width=0.5\textwidth]{robotsolution.pdf}
	\caption{PRM generated collisionfree movement for a 4-axis robot}
\end{wrapfigure}

Tests have been made for a scenario with a robot with 4 joints. For creating and plotting the environment and the resulting trajectories, Matlab functions are provided.

@@

	- dependant on density of nodes: how many neighbors have to be tested per connection
